The yaq Project: a Protocol for Scientific Instrumentation

### 2022-04-04 paper.tex

There are several large exisiting open source hardware interface projects [cite EPICS, TANGOS, pymodaq, other].
These projects are impressive at facility scale, but in our experience these do not scale well to single-investigator lab environments.
We have aimed to keep yaq as simple as possible, with the goal of staying easy to manage at very small scales without dedicated staff.
Certainly yaq lacks features compared to these exisiting projects, as we will highlight.

@@

Bridging to larger open source control layers.

@@

>>>>

There are several large exisiting open source hardware interface projects, such as EPICS \cite{DalesioLR1991a}, TANGO \cite{tango-controls.org}, and pymodaq \cite{WeberSebastien2021a}.
These projects are impressive at facility scale, but in our experience these do not scale well to single-investigator lab environments.
We have aimed to keep yaq as simple as possible, with the goal of staying easy to manage at very small scales without dedicated staff.
Certainly yaq lacks features compared to these exisiting projects, as we will highlight.

@@

Bluesky is an extensive open source control layer \cite{AllanDanielB2019a}.
Bridging to larger open source control layers.

@@

\clearpage
\bibliographystyle{unsrt}
\bibliography{references}
